\section{Projects}

%%% ----- Best way to write items (Credit - FAANGPath)
        % \item Achieved X\% growth for XYZ using A, B, and C skills.
        % \item Led XYZ which led to X\% of improvement in ABC
        % \item Developed XYZ that did A, B, and C using X, Y, and Z. 


%%%%%%% ----------------------------------- Sentiment Analysis ----------------------------------- %%%%%%%
\subsection*{AIdea Movie Review Sentiment Analysis \hfill June 2021 --- Present} 
\begin{zitemize}
    \item Achieve \textbf{Top-1 F-1 score (99.286\%)} in public leaderboard.
    \item Apply MLOps framework to organize data and model iterations.
    \item Thoroughly conduct experiments from term-based models to deep-learning-based models. Achieved highest rank with the ensemble of BERT-based models.
\end{zitemize}


%%%%%%% ----------------------------------- Impactio ----------------------------------- %%%%%%%
\subsection*{Impactio \hfill August 2020 --- March 2021} 
    \begin{zitemize}
        \item Develpoed social network for academic researchers with \textbf{GraphQL backend}.
        \item Achieved \textbf{10\% performance improvement} with optimized pagination method on query, and solved deep pagination problem.
        \item Achieved \textbf{30\% efficiency improvement} for asynchronous data processing pipline.
        \item Developed distributed crawling systems on Google Scholar with \textbf{Dask}.
    \end{zitemize}


%%%%%%% ----------------------------------- POS Tagging and Dependency Parsing ----------------------------------- %%%%%%%
\subsection*{Part-of-Speech Tagging and Dependency Parsing \hfill October 2018 --- May 2019} 
    \begin{zitemize}
        \item Achieved \textbf{11\% LAS accuracy improvement} on Universal Dependency 2.0 dataset with joint model of pos tagging and dependency parsing.
        \item Ablation tests revealed that the dependency parsing model without part-of-speech resulted in \textbf{10\% accuracy degradation}. Proved the importance of pos to dependency parsing.
    \end{zitemize}


%%%%%%% ----------------------------------- Joint Representations of Knowledge Entities and Texts ----------------------------------- %%%%%%%
\subsection*{Joint Representations of Knowledge Entities and Texts \hfill January 2018 --- December 2018} 
    \begin{zitemize}
        \item Achieved \textbf{10\% pearson correlation improvement} on SemEval-2017 Track 4a cross-lingual semantic textual similarity task.
        \item Built a comparable bilingual corpus with \textbf{distant supervision} on Wikipedia, and contributed the dataset.
        \item Proposed a cross-lingual information retrieval task to measure cross-lingual textual similarity, and achieved \textbf{30\% Top-10 accuracy increase} than the strongest cross-lingual representations method.
    \end{zitemize}


%%%%%%% ----------------------------------- News Miner ----------------------------------- %%%%%%%
\subsection*{News Miner \hfill September 2016 --- September 2017} 
    \begin{zitemize}
        \item Developed news trend analysis application with incremental clustering algorithm. Reduced the \textbf{time complexity from square to linear}.
        \item Improved searching results with optimized vector-based textual similarity calculation method.
        \item Developed dependency parsing tools with rnn-based model. Processed 1K+ sentences per MIN.
    \end{zitemize}
